Title?

### 2019-08-21 save.tex
On hold.

%\documentclass[journal,comsoc]{IEEEtran}
\documentclass[sigconf, anonymous]{acmart}

@@

\usepackage{enumerate}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs} % to use mathscr fonts

\usepackage{multicol}
\usepackage{url}

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}
\usepackage{algorithm}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\newcommand{\g}{\sigma}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corFollary}{Corollary}[section]
\newtheorem{sublemma}{Lemma}[lemma]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

%---------------ACM CCS---------------------%
\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
\acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
%-------------------------------------------%

@@

%Verizon and At\&T, two major Internet service providers (ISPs), are offering
%shared data plans, where multiple users may purchase and share a single pool of
%data. 
We investigate data-exchange platforms for wireless users. The
2cm (2nd exchange market) creates a secondary market where users can buy and sell data from each other.
The ISP owns and moderates 2cm, which prevents the secondary market from
acting as a competitor, and provides the ISP with free market research.
Competition is desired, as it provides incentive for the ISP to protect
and care for its end users.
In this work, we design a strategy space, and a distributed Progressive Second Price (PSP) mechanism
that extends individual privacy to the global space, allowing a secondary market to compete with its parent ISP. 
The PSP auction has a single degree of freedom, the reserve price. We suggest
that data exchange markets allow for greater flexibility in mechanism
design due to the connectedness of the wireless network, and the fact that data
exchange is a pure ``point of sale" market.
We propose additional degrees of freedom, and derive modifiers
to represent the deformation of the strategy space. 
Using a game theoretic analysis, we derive a new strategic
framework, removing restrictions that are dependent only on bandwidth. We
model user valuation as a strategic response to market dynamics, and propose
the resulting self-contained, self-balancing pricing system. 
We examine mutations in market dynamics resulting from the new modifiers, and
using set theory, we prove that the symmetry of our strategy space provides built-in
conditions for convergence, and upholds the properties of truthfulness, efficiency and
incentive compatibility, arriving at a Nash equlibirium.
\end{abstract}

\iffalse
We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
\fi

@@

In this work, we propose a PSP auction mechanism for a secondary data
market's valuations to be hidden from its parent ISP.
A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state, no single entity holds a global market knowledge. We consider the multi-auction, where there are many auctioneers, each holding
thier own local auction. The auction mechanism may be described as
pure-strategy progressive game with incomplete, but perfect information.

In a PSP mechanism, bids consist of (1) a quantity and
(2) a unit-price. Buyers submit bids until an
($\epsilon$-Nash) equilibrium is reached.

In the distributed setting, we assume users have a binary type, either seller,
i.e. auctioneer, or buyer, and so user strategy changes according to the user
type.

We use game theory to show that the PSP mechanism, when applied to a
pure ``point-of-sale" market, results in a primary
$\epsilon$-Nash market equilibrium that is the dominant strategy in the
multi-auction system.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology. The market
topology and the user strategy are organically determined by the impact of user
behavior on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fufills an additional property of
economy over time and space. We further model the ISP as a deaf and blind
user, who nonetheless holds the power to create a monopoly, thereby providing a free
market space in which the market may operate, and real-world implications.

The market strategy is based on providing users with an incentive framework, and
so rational users choose a collaborative exchage. 
%\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
%restrictions introduced by the CMHK secondary market. We reserve this for
%future work.
In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspendence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves. \\ 
\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
from mechanism design and game theory, respectively.\\
\iffalse
We claim that our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem. 
\fi

The user strategies are organic in that they are natural, or
induced by the dynamic market itself. In other words, adhering to the second-price rule,
where price is derived from autonomous demand, we have a strategic
progressive auction, and a multi-objective equilibria.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, (OWN WORDS) where each user
message defines a strategic point, which we may interpret as a move to a better
market position. Then, in the limit of the data-model, a user reveals its
valuation of a quantitiy of data-resource over the whole range of possible demands.

The secondary market applies the PSP auction rules over a wireless network. The
wireless users' data incentives create a pure ``point-of-sale" market. We prove
that there exists a primary $\epsilon$-Nash market equilibrium that is
the dominant strategy in the multi-auction system.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology. The market topology and the user strategy are organically determined by the impact of user
behavior on market dynamics. We determine a globally optimal objective, and a
strategy that satisfies the desires properties of competition, and
economy over time and space.

We address several topics under discussion in the real-monetary market of virtual
data ownership. The proliferation of services that are moving from grid-based to node-based communication
calls for algorithms designed for optimization in this space. Direct and
network-based communication between mobille devices allows for a simple
mutation of classic optimization models.

The secondary market provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that a secondary market
approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
as they have historically come close to monopolizing regional markets, leading
to consumer abuse. Our mechanism
takes advantage of the opportunity for full generalization provided by CMHK.
Our secondary market is adapted from the idea behind 2cm, the goal of allowing
users to buy and sell data. We claim that it is simple
to adapt our mechanism to the data share
plans published by any major ISP, for example AT\&T's data share plan \cite{att}.
We argue that data-sharing plans in general may be
biased against the end-user. Adding devices to a shared-data plan includes a
base fee for other services that have relatively small demand in comparison to
the demand for data. Effectively, users must pay for services that go unused in
order to increase the amount of data for a shared plan. Flexible data-sharing
plans are similar to the CMHK market, where a limited number of devices may
share a single data plan. A shared-data plan, however limited, offers better economy
by creating primary users with a service package with a lot of data, and
limited number of secondary users that are only using data \cite{att}.
The CMHK model allows for primary and secondary users to freely correspond,
without the restriction of a static primary-secondary user association.
This effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legistature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.
The paper is organized as follows... (TODO)

@@

%\iffalse
\section{Distributed Progressive Second Price Auctions}

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers.

We begin with a brief introduction to the distributed PSP auction for bandwith
sharing, first introduced by Lazar and Semret \cite{lazar}.
We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents. 
Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
bids $s_{-i}$,
user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
and is a Nash move
where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
budget, and every user has an elastic demand function.
Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
allocations awarded in auction $j$. 
An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg( d_i^j, 
    D_i^j(p_i^j,s_{-i}^j)\bigg).
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
{
\definition{(Nash Equilibrium)}
A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
profile $s$,
from which no player has a unilateral incentive to deviate (Johari, 2004)
(EXPAND?)
}\\

The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
%\fi

@@

\subsection{The CMHK Market}

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
set of opponent profiles. We assume that the users are connected.
A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. We assume
that users are selfish, and therefore rational. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$.
We further show that user valuation satisfies the conditions for an
elastic demand function.
\iffalse:
\definition{(Elastic demand) \cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
\fi
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). Thus, we may assume
that this is implied in our notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
$j$. We additionally determine that a user who does not submit a bid is holding
its previous bid, either zero or nonzero. For the purposes of our analysis, we will assume that a zero bid from a
buyer is equivalent to no bid.
A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
with the intent of offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$.

>>>>

%\documentclass[journal,comsoc]{IEEEtran}
\documentclass[sigconf, anonymous]{acmart}
%\documentclass[12pt]{article}

@@

%\usepackage{enumerate}
%\usepackage{amsmath,amsthm,amssymb}
%\usepackage{mathrsfs} % to use mathscr fonts

%\usepackage{multicol}
%\usepackage{url}

%\usepackage{epstopdf}
%\usepackage{caption,subcaption}
%\usepackage{graphicx}
%\usepackage{float}\usepackage{multicol}
%\usepackage{multirow}
%\usepackage{array}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
%\usepackage{changepage}
%\usepackage{color}
%\usepackage{listings}
%\usepackage{fancyvrb}
%\usepackage{verbatim,moreverb}
%\usepackage{courier}
\usepackage{algorithm}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\newcommand{\g}{\sigma}
\newcommand{\s}{\nu}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{sublemma}{Lemma}[lemma]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

\fi
 %\iffalse
%---------------ACM CCS---------------------%
\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
and Communications Security}{Due 8 May 2018}{Dallas, Texas}
\acmYear{2018}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
%-------------------------------------------%
%\fi

@@

%Verizon and At\&T, two major Internet service providers (ISPs), are offering
%shared data plans, where multiple users may purchase and share a single pool of
%data. 
We propose a distributed, privacy-preserving auction-based approach to
allocation in a secondary market for wireless data exchange.
The secondary market is modeled as a fully connected, pure ``point of sale"
market, with inital public platform provided by its parent wireless internet service
provider (WISP). 
The progressive second price (PSP) auction rules provide our underlying auction
structure, allowing for a single degree of freedom, the reserve
price. We suggest that data exchange markets allow for greater flexibility in
mechanism design.
We propose new, natural degrees of freedom, and derive modifiers
to represent the deformation of the strategy space.

Wireless users are modeled as a fixed type with dynamic incentives. Using a game
theoretic analyis, we derive strategy profiles for wireless users
based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
We examine mutations in the strategy space resulting from the new modifiers, and
prove that the desired PSP properties hold. 
Convergence is determined by set theory; we prove that the symmetry of our
strategy space provides built-in conditions for convergence and stablility, finally arriving at a network Nash equlibirium.

Trust and privacy issues in secondary markets have yet to be addressed.
As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
In a centrally moderated secondary market, an unregulated,
rational ISP will prevent its secondary market from acting as a competitor.
Competition is desired as it provides incentive for the ISP to protect
and care for its end users.
The distributed nature of PSP extends individual privacy to the secondary market,
allowing for it to compete with its parent ISP. 
\end{abstract}

@@

An evolving consumer culture is has led wireless internet service providers
(ISPs) to rethink their service plans. Mobile data usage is quickly outpacing voice and SMS in
wireless network, and the trend is only expected to increase with
multi-device ownership. Declining revenue has caused ISPs search for sources
of new revenue in the changing market. Thus the introduction of the shared data plan \cite{att}. Using an account
service, users are able to keep track of data usage in real time across all
their devices. 
The shared data service plan requires that users hold an \emph{a priori}
knowledge of demand.
We address several topics: data as a product in the real-monetary market, and
data a network resource in a wireless topology.

Many new services are found exclusively on mobile devices; older softwares
are moving from (wired) grid-based to node-based communication. Software-defined
networking (SDN) addresses the new environment of wireless communication
devices, allowing for a programmable network architecture. 
The account services that manage wireless shared data plans decentralize
network management, and mobility becomes a factor in SDN design.
Individual mobile devices provide flexibility, and may make decisions regarding
local network infrastructure. There is a clear need for algorithms designed for
optimization in this space. In many cases, the direct communication between
mobile devices allows for a simple mutation of classic optimization models.
Auctions are key in SDN for the fair allocation of resources. For this work, we
focus on mobile data, an infinitely divisible and distributable quantity.
Mobile data represents online data accessed using the WISP network, and as
representation of future network usage, we are able remove restrictions imposed
by the physical layer.

We focus on Vickery-Clark-Groves (VCG) type 
auction mechanisms that are (1) easily distributed, and (2) allocate an infinitely
divisible resource.
In \cite{lazar}, Lazar and Semret introduce the Distributed Progressive Second Price (PSP)
Mechanisms for bandwidth allocation. An auction mechanism is defined
as distributed when the allocations at any element depend only on
local state, no single entity holds a global market knowledge. We consider the
multi-auction, where there are many auctioneers, each holding thier own local auction.

The model for data exchange was recently adopted by China Mobile Hong Kong
(CMHK), who released a platform, 2cm (2nd exchange market) creating a secondary
market where users can buy and sell data from each other.
CMHK owns and moderates 2cm, centrally computing allocations of mobile data
based on bids submitted to the platform.
Flexible data-sharing
plans are similar to the CMHK market, where a limited number of devices may
share a single data plan. A shared-data plan, however limited, offers better economy
by creating primary users with a service package with cellular, and a lot of data, and
limited number of secondary users that are using only data \cite{att}.
The secondary market allows for primary and secondary users to freely correspond,
without the restriction of a static primary-secondary user association.

Users on the shared data plan given by \cite{att} do not ``buy" or ``sell"
data, however, we may easily augment the model to include a price function,
which may be virtual, creating a secondary market.
In order to demonstrate potential of expanding to other $\emph{a priori}$ use
models, we give a simple example. Consider Alice and Bob, who met through an online service connecting neighborly
individuals closest to each other, in fact, close enough to be within wireless
range. Alice is going on vacation, and offers to transfer her wireless signal to
Bob. As they have the same provider, Bob agrees, and is able to use Alice's
bandwidth, which he finds is useful during peak network
hours. He pays a discounted rate. We note that the additional bandwith may be
used by another device, or even a 5G-capable mobile device.

The secondary market provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that a secondary market effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legistature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.
Laws such as \cite{fedbill} exist to
regulate ISPs as they have historically come close to monopolizing regional
markets, leading to consumer abuse.
The global view of privacy has not been addressed, as the data exchange model is still
in its experimental phase.
Within the secondary market, bid privacy is a concern for two reasons: (1) Buyers are reluctant to
reveal their true valuations, as sellers may use these values to discriminate
against specific buyers. (2) Buyers doubt an auction's outcome, as they do
not pay what they bid, e.g. the auctioneer might create a fake
second highest bid slightly below the highest bid in order to increase his revenue
In general, the buyer does not trust the auctioneer, and the economy does not
trust the ISP.

We therefore determine that our mechanism must be (3) globally and locally privacy-preserving.

In a PSP mechanism, bids consist of (1) a quantity and
(2) a unit-price. Buyers submit bids until an
($\epsilon$-Nash) equilibrium is reached. 
Our mechanism
takes advantage of the opportunity for adaptation provided by the
secondary market.

The secondary market applies the PSP auction rules over a wireless network. The
wireless users' data incentives create a pure ``point-of-sale" market. We prove
that there exists a primary $\epsilon$-Nash market equilibrium that is
the dominant strategy in the multi-auction system.

The market
topology and the user strategy are organically determined by the impact of user
behavior on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fufills an additional property of
economy over time and space. To the best of our knowledge, this is the first
work to provide a comprehensive derivation of a truthful mechanism that is self-contained within a dynamic market
topology.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology.

In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspendence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves.
We claim that our formulation holds the desired PSP qualities,
converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
\epsilon I!)$.
We note that the convergence time is dependent on the ratio of
supply and demand, or the ratio of buyers to sellers.

We focus on providing users with an incentive framework, and
so rational users choose a collaborative exchage. 
The user strategies are organic in that they are natural, or
induced by the dynamic market itself. In other words, adhering to the second-price rule,
where price is derived from autonomous demand, we have a strategic
progressive auction, and a multi-objective equilibria.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, Then, in the limit of
the data-model, a user reveals its valuation of a quantitiy of data-resource over the whole range of possible demands.

We describe our auction mechanism as a
pure-strategy progressive game with incomplete, but perfect information.

The paper is organized as follows... (TODO)

@@

@@

\subsection{The Secondary Market}

We construct the model for a PSP data auction for mobile users
particpating in secondary mobile data exchange market.
Let the set of all wireless users to be labeled by
the index set $\mcI = \lbrace 1, \cdots, I\rbrace$. In our current formulation, we do not allow a seller to host multiple
auctions, thus we may assume that data is a unary resource belonging to the seller, and
identify each local auction with the index of the seller
$j\in\mcI$. The bid profiles of the users are given as,
$s \equiv
[s_i^j] \in \mcI \times \mcI$,  
We have the strategy space for buyer $i$ as all possible bids at all auctions:
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \big( \Pi_{k\ne
i\in\mcI} S_k^j\big)$ as the
associated opponent profiles. 
\iffalse
(HERE)
Additionally, we assume that a user's budget is 
sufficient, as the alternative is to pay the overage fee to the ISP, but as we
assume a rational user.
\fi

The grid of bid profiles, $s$, represents the state of distributed PSP auction
mechanism in the secondary market. 
We emphasize that we allow the grid $s$ to represent the bids of all buyers and
sellers. In general, we will not reference the full grid. In order to emphasize
that a bid belongs to a seller, we use the notation $\s_i^j$. We
will also empasize the \emph{context} of the bid to indicate the user type.
To further clarify our analysis, we adopt the notational conventions: a
seller's profile is denoted by $\s^j = [s_i^j]_{i\in\mcI}$, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyer's profile, where $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents.
Furthermore, noting that this is a simplification for ease of notation, we let
$D^j = \sum_{i\in\mcI} d_i^j$ be the total amount of data $j$ has to sell, and
$D_i = \sum_{j\in\mcI} d_i^j$ represent the total amount of data desired by buyer $i$.

We assume a public platform, published by the ISP, that allows sellers to advertise their
auctions, and that buyers may submit bids directly to sellers over the wireless
network. 
The ISP is included
by introducing a mutation of user type, and represent
the ISP as a blind, deaf user $\kappa$, who does not participate
in any auctions, but nonetheless holds the power to create a monopoly. At time
$t=0$, a seller $j$ entering the market will
submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
platform, and so the initial bid $\s_\kappa^j$, is public knowledge.

We assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). 
In general, we denote a buyer's identity $i \in \mcI$, and a seller as
$j\in\mcI$.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. 
Seller $j$'s local auction begins at time $t>0$. The seller takes reponsibility
to send opponent bid profiles $s_{-i}$ to each buyer that joins the auction,
those buyers where $s_i^j > 0 \in s$, as well its own bid, $\s_i^j = (d_i^j,
p_i^j)$, offfering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$. 
Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not recieve opponent profiles from seller
$j$. We additionally determine that a user who does not submit a bid is holding
to the previous bid, either zero or nonzero. We note that buyers are
consistently referenced using the index $i$ as a subscript, and sellers using
the index $j$ as a superscript, as in \cite{semret}.

We will examine the role of buyers, who are able to directly
influence global market dynamics, and assume that the sellers take a reactionary role.
Each buyer $i$ will have information from each seller $j$, as well as opponent
profiles $s_{-i}$, from each auction in which it is participating.
In the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access all buyer profiles, $[s_1, \cdots, s_I]$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
Finally, we define the seller pool for buyer $i\in\mcI$: 
% MIN SET
$$
    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} D^j,
$$
and similarly, for a seller $j\in\mcI$, we define the set of participating buyers:
$$
    \mcI^j(m) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
m}\sum_{i\in{\mcI}'} p_i^j,
$$
where $m, n\in\mcI$.
